% THIS DOCUMENT IS FOLLOWS THE VOLERE TEMPLATE BY Suzanne Robertson and James Robertson
% ONLY THE SECTION HEADINGS ARE PROVIDED
%
% Initial draft from https://github.com/Dieblich/volere
%
% Risks are removed because they are covered by the Hazard Analysis
\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,      % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\newcommand{\lips}{\textit{Insert your content here.}}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software} 
\author{\authname}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\textbf{Date}} & {\textbf{Version}} & {\textbf{Notes}}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\\

~\newpage
\section{Purpose of the Project}
\subsection{User Business}
\lips
\subsection{Goals of the Project}
\lips
\section{Stakeholders}
\subsection{Client}
The client is the faculty supervisor of this project, Dr. Martin Von Mohrenschildt. With direct research interests in signal processing and a personal interest in how it relates to 
music, he is investing his own time in the development of the product.
\subsection{Customer}
The archetypal customer is a musician of any skill level, with emphasis based on musicians who have little-to-no music theory knowledge. The customer will utilize the application 
to quickly produce sheet music for either original compositions or existing songs. 
\subsection{Other Stakeholders}
\begin{itemize}
  \item \textbf{Software developers:} Provide the technical knowledge and skill to design and build the system.
  \item \textbf{Composers:} As SMEs, provide the music theory knowledge needed to make the system useful for the customer.
  \item \textbf{Users of music-annotating software:} As SMEs, provide opinions on the features they like or dislike about existing music-annotating softwares. This will help inform the developers on which features of the product to prioritize.
  \item \textbf{Music teachers:} Provide similar support to students that may be replaced by usage of this product. They will have a vested interest in ensuring this product does not encourage bad composing habits in users of the product.
  \item \textbf{Music students:} Similar to the Composers, they will provide the music theory knowledge needed to make the system useful for the customer. However, their input will be from the same learning point of view as the expected user, and thus will have a higher degree of influence on the product.
  \item \textbf{IP lawyers:} Will ensure this product follows fair use and does not infringe on copyrights.
  \item \textbf{Dr. Spencer Smith:} As the course instructor, the performance and outcome of this product will be a direct reflection of his role in the capstone course.
\end{itemize}
\subsection{Hands-On Users of the Project}
\subsubsection*{User Category 1: Beginner Musicians}
\textbf{User Role:} Use this product to create sheet music, either as a learning aid or as a quick alternative to learning music notation.\\
\textbf{Subject matter experience*:} Novice - Little experience with music theory, but likely have a moderate knowledge of music in practicality (i.e., playing an instrument or listening to music). \\
\textbf{Technological experience*:} Novice - May or may not have limited experience with other music-annotating softwares. \\
\textbf{User characteristics:} 
\begin{itemize}
  \item Little to no music theory knowledge
  \item Passionate about music
  \item All ages (i.e., both children and adults)
  \item New to playing instruments
  \item Not comfortable with complex software
  \item Eager to learn
  \item Less willing to spend money
\end{itemize}

\subsubsection*{User Category 2: Composers}
\textbf{User Role:} As masters of music notation and composition, this group will use the product as a practice aid or to quickly make note of composition ideas. \\
\textbf{Subject matter experience*:} Master - have spent years learning and practicing music theory and composition. \\
\textbf{Technological experience*:} Journeyman to Master - Have experience with music-annotating software but haven't necessarily used them extensively. \\
\textbf{User characteristics:}
\begin{itemize}
  \item Advanced music theory knowledge
  \item Passionate about music
  \item 25+ years old
  \item Have a hard time learning new technologies
  \item Willing to spend money
\end{itemize}
\noindent
\textit{*User experience level may be rated as one of novice, journeyman, or master.}

\subsection{Personas}
Harold Style is a software engineering student at McMaster University with a deep interest in music, and loves playing the guitar. Despite his lack of a formal music education, 
he has perfect pitch and thus learns songs by listening to them rather than learn how to read sheet music. However, he recently joined a local rock band called The Beetles who 
expect him to contribute during their songwriting sessions. He needs a quick way to produce sheet music for his own compositions, as well as learn to read the scores written by 
his bandmates. As a future software engineer he enjoys learning new technologies that can make his life easier, and he dislikes reading of any sort.
\subsection{Priorities Assigned to Users}
\textbf{Key users:} Beginner musicians
\textbf{Secondary users:} Composers.
\subsection{User Participation}
Beginner musicians will have a high level of participation in the creation of system requirements. Their feedback will be especially essential during the early to middle development phases to ensure that the system meets their various needs for simplicity, intuitive design/usage, and music theory assistance.
Composers will have a moderate level of participation in the creation of system requiremens, slightly less than that of the Beginner Musician group. Their subject matter expertise will be useful in creating relevant requirements to ensure precision of audio transcription and its overall score editing capabilities.
\subsection{Maintenance Users and Service Technicians}
This product will be maintained by a software development team, consisting of software developers, UI/UX designers, test engineers, and a project manager. 
Users will receive product support directly from the customer support team, and IP lawyers will be engaged as necessary to address matters of intellectual property.

\section{Mandated Constraints}
\subsection{Solution Constraints}
\lips
\subsection{Implementation Environment of the Current System}
\lips
\subsection{Partner or Collaborative Applications}
\lips
\subsection{Off-the-Shelf Software}
\lips
\subsection{Anticipated Workplace Environment}
\lips
\subsection{Schedule Constraints}
\lips
\subsection{Budget Constraints}
\lips
\subsection{Enterprise Constraints}
\lips

\section{Naming Conventions and Terminology}
\subsection{Glossary of All Terms, Including Acronyms, Used by Stakeholders
involved in the Project}
\lips

\section{Relevant Facts And Assumptions}
\subsection{Relevant Facts}
\lips
\subsection{Business Rules}
\lips
\subsection{Assumptions}
\lips

\section{The Scope of the Work}
\subsection{The Current Situation}
\lips
\subsection{The Context of the Work}
\lips
\subsection{Work Partitioning}
\lips
\subsection{Specifying a Business Use Case (BUC)}
\lips

\section{Business Data Model and Data Dictionary}
\subsection{Business Data Model}
\lips
\subsection{Data Dictionary}
\lips

\section{The Scope of the Product}
\subsection{Product Boundary}
\lips
\subsection{Product Use Case Table}
\lips
\subsection{Individual Product Use Cases (PUC's)}
\lips

\section{Functional Requirements}
\subsection{Audio Input Handling}
\subsubsection*{FR-AI1 Audio Formats}
\textbf{Requirement:} The system shall accept audio input from users in various formats (e.g., WAV, MP3, AAC). \\
\textbf{Fit Criterion:} The system confirms a succesful upload.
\subsubsection*{FR-AI2 Audio Recording}
\textbf{Requirement:} The system shall provide a user interface for recording audio directly through a microphone connected to the user's device. \\
\textbf{Fit Criterion:} The system displays a confirmation of reception during real-time recording.
\subsubsection*{FR-AI3 Audio Uploads}
\textbf{Requirement:} The system shall allow users to upload pre-recorded audio files. \\
\textbf{Fit Criterion:} The system confirms reception of the pre-recorded audio file.
\subsubsection*{FR-AI4 User Input}
\textbf{Requirement:} The user shall give their instrument (i.e., piano or guitar) to the system as input. \\
\textbf{Fit Criterion:} The interface and concert pitch of the generated sheet music reflect the user's choice.

\subsection{Signal Processing}
\subsubsection*{FR-SP1 Noise Reduction}
\textbf{Requirement:} The system shall perform noise reduction on the audio input to enhance quality. \\
\textbf{Fit Criterion:} The system generates identical sheet music for input with no background noise and input with a 10\% increase in background noise.
\subsubsection*{FR-SP2 Note Identification}
\textbf{Requirement:} The system shall analyze the audio to identify pitch and rhythm. \\
\textbf{Fit Criterion:} The generated sheet music visually matches expected notes from a reference audio source and corresponding sheet music.
\subsubsection*{FR-SP3 Key and Time Signature Identification}
\textbf{Requirement:}	The system shall analyze the audio to identify the key and time signatures. \\
\textbf{Fit Criterion:} The system correctly identifies key and time signatures or their equivalencies (e.g. a minor to C major, common time to cut time) from a reference audio source and corresponding sheet music.
\subsubsection*{FR-SP4 Processing Limitations}
\textbf{Requirement:} The system gracefully handles overly complex audio input (i.e., it is unable to perform accurate signal processing). \\
\textbf{Fit Criterion:} The system notifies the user that their input cannot be processed.
\subsubsection*{FR-SP5 Polyphonic Audio}
\textbf{Requirement:} The system shall handle polyphonic audio, allowing for multiple notes to be detected simultaneously. \\
\textbf{Fit Criterion:} The generated sheet music contains chords/simultaneous melody.
\subsubsection*{FR-SP6 Monophonic Audio}
\textbf{Requirement:} The system shall handle monophonic audio. \\
\textbf{Fit Criterion:} The generated sheet music contains single pitch notes.

\subsection{Sheet Music Generation}
\subsubsection*{FR-SMG1 Notation}
\textbf{Requirement:} The system shall generate sheet music in standard music notation based on the parsed audio data. \\
\textbf{Fit Criterion:} The generated sheet music is visually comparable to a reference piece of sheet music.
\subsubsection*{FR-SMG2 Concert Pitch}
\textbf{Requirement:} The system shall generate sheet music in the concert pitch of the instrument played in the audio input. \\
\textbf{Fit Criterion:} The generated sheet music visually matches expected notes from a reference audio source and corresponding sheet music.
\subsubsection*{FR-SMG3 Post-Processing Edits}
\textbf{Requirement:} The system shall allow users to view and edit the generated sheet music within the application. \\
\textbf{Fit Criterion:} Changes made by the user are reflected in the output files produced during sheet music generation.

\subsection{User Interface}
\subsubsection*{FR-UI2 System Feedback}
\textbf{Requirement:} The interface shall display processing feedback during audio input. \\
\textbf{Fit Criterion:} Feedback from system is displayed to the user within 2 seconds of their input.
\subsubsection*{FR-UI3 System Documentation}
\textbf{Requirement:} The system shall provide help documentation and user guides for each feature. \\
\textbf{Fit Criterion:} At least 90\% of users during user testing find the interface easy to navigate.
\subsubsection*{FR-UI4 User Feedback}
\textbf{Requirement:} The system shall provide a feedback mechanism for users to report issues or suggest features. \\
\textbf{Fit Criterion:} The development team successfully receives user feedback via the feedback mechanism 100\% of the time.
\subsubsection*{FR-UFI5 Customer Support}
\textbf{Requirement:} The system shall include customer support contact information for troubleshooting. \\
\textbf{Fit Criterion:} At least 90\% of users during user testing report successfull interactions with customer support.

\subsection{Save and Load}
\subsubsection*{FR-SL1 Save}
\textbf{Requirement:} The system shall allow users to save their work, including both audio files and generated sheet music. \\
\textbf{Fit Criterion:} 100\% of the time when the system reports a succesfull save, the user is succesfully able to locate the audio files and generated sheet music.
\subsubsection*{FR-SL2 Load}
\textbf{Requirement:} The system shall support loading previously saved audio files and generated sheet music for further editing. \\
\textbf{Fit Criterion:} The system sucesfully retains user progress such that the user may return to their unfinished work seamlessly.


\section{Look and Feel Requirements}
\subsection{Appearance Requirements}
\lips
\subsection{Style Requirements}
\lips

\section{Usability and Humanity Requirements}
\subsection{Ease of Use Requirements}
\lips
\subsection{Personalization and Internationalization Requirements}
\lips
\subsection{Learning Requirements}
\lips
\subsection{Understandability and Politeness Requirements}
\lips
\subsection{Accessibility Requirements}
\lips

\section{Performance Requirements}
\subsection{Speed and Latency Requirements}
\subsubsection*{PR-SL1 User Interface Response Time}
\textbf{Requirement:} The interface between the user and the sheet music generator app shall respond within a reasonable time when processing input or selecting menu options.\\
\textbf{Fit Criterion:} The product shall respond in less than 2 seconds for 90 percent of user interactions. No response shall take longer than 5 seconds.
\subsubsection*{PR-SL2 File Import and Export Speed}
\textbf{Requirement:} The app shall import and export music files within a reasonable time for files up to 100MB in size.\\
\textbf{Fit Criterion:} For files up to 100MB, the app shall import and export them within a reasonable time frame for their system for more than 95 percent of operations.

\subsection{Safety-Critical Requirements}
\subsubsection*{PR-SC1 Epilepsy Safety}
\textbf{Requirement:} The app shall not display rapid flashing lights, animations, or any visual effects that could trigger epileptic seizures in users.\\
\textbf{Fit Criterion:} The app’s graphical interface must comply with WCAG 2.1 (Web Content Accessibility Guidelines) for flashing content, limiting visual effects to fewer than 3 flashes per second. The interface will be tested with accessibility tools to ensure compliance with these standards.
\subsubsection*{PR-SC2 Instrument Input Setup}
\textbf{Requirement:} The app shall guide users through the correct setup of instrument input to prevent audio misconfiguration, damage to the user/instrument, and damage to the application’s device.\\
\textbf{Fit Criterion:} The app will include an interactive, step-by-step tutorial for configuring instrument inputs (via external devices or microphones). The setup process should be completed with a 95\% success rate based on user testing, ensuring correct audio input detection on the first attempt.

\subsection{Precision or Accuracy Requirements}
\subsubsection*{PR-PA1 Pitch Detection Accuracy}
\textbf{Requirement:} This app shall correctly detect musical pitch from instruments' input to ensure that all notes are transcribed correctly.\\
\textbf{Fit Criterion:} The app must maintain this pitch accuracy over all test cases involving diverse instruments and note ranges, with no more than 1\% error. Also must satisfy requirement OE-EP1 for noise tolerance.
\subsubsection*{PR-PA2 Timing Accuracy}
\textbf{Requirement:} The app shall accurately capture note durations and rhythms within a reasonable tolerance to ensure correct rhythmic transcription.\\
\textbf{Fit Criterion:} The app must maintain timing accuracy within the 100ms across all test cases.

\subsection{Robustness or Fault-Tolerance Requirements}
\subsubsection*{PR-RFT1 Reliability (Time Between Failures)}
\textbf{Requirement:} The app shall operate continuously for at least 24 hours between failures or system crashes, ensuring that users experience minimal interruptions during usage.\\
\textbf{Fit Criterion:} The app must pass reliability testing by operating under typical usage conditions for 24 hours without a failure in at least 95\% of test cases.
\subsubsection*{PR-RFT2 Availability (Uptime)}
\textbf{Requirement:} The app shall achieve 99.5\% uptime, ensuring that it is available for use at nearly all times, excluding brief periods for necessary updates or maintenance.\\
\textbf{Fit Criterion:} The app must demonstrate an average of 99.5\% uptime over a reasonable time.
\subsubsection*{PR-RFT3 Crash Recovery}
\textbf{Requirement:} In an unexpected crash, the app shall automatically save the user’s current session, including any partially transcribed sheet music, and allow the user to recover their work upon restart.\\
\textbf{Fit Criterion:} During testing, the app must successfully recover user data in 98\% of cases where a crash occurs, with no data loss.
\subsubsection*{PR-RFT4 Performance Under Load}
\textbf{Requirement:} The app shall maintain reliable performance under conditions of high user activity (e.g., processing complex polyphonic inputs or large files) without significant slowdowns or crashes.\\
\textbf{Fit Criterion:} The app must maintain stable performance, with no more than a 30\% decrease in processing speed, when tested under maximum expected load conditions.
\subsubsection*{PR-RFT5 Handling Signal Interruptions}
\textbf{Requirement:} The app shall continue to operate and retain the audio signals received up to the point of interruption, even if the instrument input is temporarily lost (e.g., due to cable disconnection or microphone failure).\\
\textbf{Fit Criterion:} The app must store buffered audio data for up to 2 minutes during signal interruptions and automatically resume transcription once the input is restored, with 0\% data loss in at least 95\% of test cases.
\subsubsection*{PR-RFT6 Graceful Degradation}
\textbf{Requirement:} In the event of a performance slowdown (e.g., due to excessive input data or limited system resources), the app shall degrade its services gracefully by notifying the user of delays without crashing.\\
\textbf{Fit Criterion:} During stress testing under heavy load (e.g., multiple instruments or large file sizes), the app must maintain operational status and notify the user of delays or lowered performance within 5 seconds of detection, with no system crashes in 99\% of test cases.
\subsubsection*{PR-RFT7 Automatic Recovery from Software Glitches}
\textbf{Requirement:} If the app encounters a minor software error (e.g., unexpected input format or corrupted file), it shall log the error, notify the user, and continue functioning by skipping the problematic section rather than halting it.\\
\textbf{Fit Criterion:} The app must pass testing by handling minor software errors in at least 90\% of cases without crashing and will log the issue for future debugging.

\subsection{Capacity Requirements}
\subsubsection*{PR-C1 Audio Input Capacity}
\textbf{Requirement:} The app shall process audio input of up to 90 minutes of continuous recording in a single session without performance degradation.\\
\textbf{Fit Criterion:} The app must be tested with audio recordings of varying lengths (up to 90 minutes) and successfully process and transcribe the entire duration with no more than a 5\% slowdown in transcription speed or accuracy.
\subsubsection*{PR-C2 Simultaneous User Sessions}
\textbf{Requirement:} The app shall support at least 10 simultaneous user sessions (local or cloud-based) without degradation in performance or delays in processing.\\
\textbf{Fit Criterion:} During testing with 10 simultaneous active user sessions, the app must maintain performance levels, including stable response times and transcription accuracy, with no noticeable slowdown in 95\% of test cases.

\subsection{Scalability or Extensibility Requirements}
\subsubsection*{PR-SE1 User Base Growth}
\textbf{Requirement:} The app shall be capable of scaling to support an increase in the user base to 1000 users without requiring major architectural changes to support a change from personal to commercial use.\\
\textbf{Fit Criterion:} The app’s infrastructure must be designed to scale up by a factor of 10 and should undergo stress testing to ensure it can handle 1000 simultaneous user sessions with no significant performance degradation.
\subsubsection*{PR-SE2 Feature Extensibility}
\textbf{Requirement:} The app shall be designed with a modular architecture that allows for future feature additions, such as multi-instrument detection or cloud-based collaboration tools, without requiring significant refactoring.\\
\textbf{Fit Criterion:} The app must pass code reviews and architecture validation to ensure it can integrate additional modules or features within 6 months of the product’s initial release, with minimal impact on core functionalities.
\subsubsection*{PR-SE3 Processing Power for Complex Music Compositions}
\textbf{Requirement:} The app shall be built to be able to scale its processing capabilities to handle future complex compositions involving multiple simultaneous instrument tracks supporting growth for polyphony.\\
\textbf{Fit Criterion:} During testing, the app must demonstrate the ability to process increasingly complex musical arrangements.

\subsection{Longevity Requirements}
\subsubsection*{PR-L1 Expected Lifetime}
\textbf{Requirement:} The app shall be designed to operate effectively with regular software updates and minor maintenance for a minimum of five years without requiring a major rewrite or overhaul.\\
\textbf{Fit Criterion:} The app’s development roadmap must include planned updates and feature expansions to maintain functionality and relevance for at least five years after launch.

\section{Operational and Environmental Requirements}
\subsection{Expected Physical Environment}
\subsubsection*{OE-EP1 Operating Environment}
\textbf{Requirement:} The app shall be used on personal computers or laptops in typical indoor environments, such as home studios, classrooms, or offices. It should perform well under varying levels of ambient noise.\\
\textbf{Fit Criterion:} The app must be tested in multiple indoor settings and perform well without requiring any environment-specific adjustments.
\subsubsection*{OE-EP2 Noise and Audio Input Quality}
\textbf{Requirement:} The app shall be able to capture clear audio input in environments with moderate ambient noise, such as home studios or cafes, without significant degradation in transcription accuracy.\\
\textbf{Fit Criterion:} The app must be tested in environments with background noise to ensure that it can still accurately capture and process audio inputs without more than a 5\% drop in accuracy.
\subsubsection*{OE-EP3 Workspace Flexibility}
\textbf{Requirement:} The app shall be usable on laptops with limited screen space, such as 13-inch displays, and must adjust its layout to accommodate various screen resolutions and sizes.\\
\textbf{Fit Criterion:} The app must be tested on screens ranging from 13 inches to 27 inches, with functionality and UI usability maintained across all screen sizes and resolutions.
\subsubsection*{OE-EP4 Portable Setup Compatibility}
\textbf{Requirement:} The app shall be compatible with portable setups, such as laptops used in temporary workspaces like cafes or live performance venues, ensuring that it can be used effectively in different environments without special hardware.\\
\textbf{Fit Criterion:} The app must function smoothly on portable setups with wireless internet and standard laptop hardware, and be tested for usability in transient environments where quick setup and breakdown are required.

\subsection{Wider Environment Requirements}
\subsubsection*{OE-WE1 General Hardware}
\textbf{Requirement:} The app shall operate effectively on devices with varying interface specifications.\\
\textbf{Fit Criterion:} The app must be tested on screens ranging from 13 inches to 27 inches, with functionality and UI usability maintained across all typical screen sizes and resolutions.

\subsection{Requirements for Interfacing with Adjacent Systems}
\subsubsection*{OE-IA1 Audio Input Devices}
\textbf{Requirement:} The app shall interface with standard audio input devices, including USB microphones, instrument pickups, and built-in computer microphones.\\
\textbf{Fit Criterion:} The app must support audio input via devices adhering to USB Audio Class 1.0 and higher, and be tested with common setups (e.g., USB microphones, line-in jacks).\\
\subsubsection*{OE-IA2 Audio File Import and Export}
\textbf{Requirement:} The app shall interface with common audio file formats for both import and export, including WAV and MP3.\\
\textbf{Fit Criterion:} The app must successfully import and export audio files in WAV (PCM), and MP3 (MPEG-1 Layer III).\\
\subsubsection*{OE-IA3 Music Notation Software Integration}
\textbf{Requirement:} The app shall export sheet music in formats compatible with popular music notation software, including MusicXML and MIDI files.\\
\textbf{Fit Criterion:} The app must generate MusicXML and MIDI files compatible with the software.\\

\subsection{Productization Requirements}
\subsubsection*{OE-P1 Distribution}
\textbf{Requirement:} The app shall be distributed as a downloadable executable file.\\
\textbf{Fit Criterion:} The app must be packaged in an installer that can be downloaded from a website or software repository, with no additional dependencies required for installation.
\subsubsection*{OE-P2 Installation Process}
\textbf{Requirement:} The product shall be capable of being installed by an untrained user with minimal technical knowledge, requiring minimal steps from download to full installation.\\
\textbf{Fit Criterion:} The installation wizard must guide the user through the process, providing automatic configuration options and requiring minimal user input. Instructions must be included within the installer interface.
\subsubsection*{OE-P3 Size and Compatibility}
\textbf{Requirement:} The app’s installation file size shall not exceed 500MB, ensuring that the product can be easily downloaded even with moderate internet connections.\\
\textbf{Fit Criterion:} The app must be easily installed on a variety of systems.
\subsubsection*{OE-P4 Post-Installation Configuration}
\textbf{Requirement:} The product shall configure its default settings upon installation, but allow users to modify these settings (e.g., input source, output format) during or after the installation process.\\
\textbf{Fit Criterion:} A settings configuration panel must be accessible from the app's user interface, allowing users to adjust settings without needing to edit configuration files manually.

\subsection{Release Requirements}
\subsubsection*{OE-R1 Initial Release}
\textbf{Requirement:} The first stable version of the app shall be released within the timeline of this capstone course after completing the testing and POC phase. This release will include core functionality such as converting instrument signals to sheet music and basic editing capabilities.\\
\textbf{Fit Criterion:} The initial release must undergo testing and pass all quality assurance checks. Core features must be fully operational, and the product should be ready for general use without major bugs.

\section{Maintainability and Support Requirements}
\subsection{Maintenance Requirements}
\lips
\subsection{Supportability Requirements}
\lips
\subsection{Adaptability Requirements}
\lips

\section{Security Requirements}
\subsection{Access Requirements}
\lips
\subsection{Integrity Requirements}
\lips
\subsection{Privacy Requirements}
\lips
\subsection{Audit Requirements}
\lips
\subsection{Immunity Requirements}
\lips

\section{Cultural Requirements}
\subsection{Cultural Requirements}
\lips

\section{Compliance Requirements}
\subsection{Legal Requirements}
\lips
\subsection{Standards Compliance Requirements}
\lips

\section{Open Issues}
\lips

\section{Off-the-Shelf Solutions}
\subsection{Ready-Made Products}
\lips
\subsection{Reusable Components}
\lips
\subsection{Products That Can Be Copied}
\lips

\section{New Problems}
\subsection{Effects on the Current Environment}
\lips
\subsection{Effects on the Installed Systems}
\lips
\subsection{Potential User Problems}
\lips
\subsection{Limitations in the Anticipated Implementation Environment That May
Inhibit the New Product}
\lips
\subsection{Follow-Up Problems}
\lips

\section{Tasks}
\subsection{Project Planning}
\lips
\subsection{Planning of the Development Phases}
\lips

\section{Migration to the New Product}
\subsection{Requirements for Migration to the New Product}
\lips
\subsection{Data That Has to be Modified or Translated for the New System}
\lips

\section{Costs}
\lips
\section{User Documentation and Training}
\subsection{User Documentation Requirements}
\lips
\subsection{Training Requirements}
\lips

\section{Waiting Room}
\lips

\section{Ideas for Solution}
\lips

\newpage{}
\section*{Appendix --- Reflection}

\input{../Reflection.tex}

\input{../SRS_Reflection.tex}

\end{document}